TR Invariant T.I.

### 2017-04-27 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] Use SS.Qing's formula to get Chern number. And plotted Chern number v.s. different m.

    The surface of $\vec{d}$ as $p_x,p_y$ varies is somewhat distorted
    (fig~\ref{fig:BerryPhase/Shape}). Thankfully, it does not change as $m$
    varies (fig~\ref{fig:BerryPhase/AsMVaries}). Also, it is easy to see that
    when $m<0$ or $m>4$, the surface does not cut the $xy$ plane, hence in that
    region the Berry Phase is trivial. The distorted picture is dispatched into
    4 different pieces in fig~\ref{fig:BerryPhase/attempts}. It could be
    imagined that the vector $\vec{d}$ goes in the order: red
    $\to$blue$\to$yellow$\to$green$\to$red. With this and a little bit of
    imagination, I since the solid angle $\Omega$ when $0<m<2$ and $2<m<4$ are
    both $4\pi$.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.5\linewidth]{pics/BerryPhase/Shape.pdf}
        \caption{Surface formed as $p_x,p_y$ varies}
        \label{fig:BerryPhase/Shape}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/AsMVaries.pdf}
        \caption{As $m$ varies, the shape does not change. The blue plane is the
        $xy$ plane. The center of that surface meets the $xy$-plane when $m=2$.
        That surface leaves the $xy$-plane when $m<0$ or $m>4$.}
        \label{fig:BerryPhase/AsMVaries}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/attempts.pdf}
        \caption{Attempts to determine the Berry phase by dispatching the surface
        into 4 different patches ($m=2$)}
        \label{fig:BerryPhase/attempts}
    \end{figure}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\bibliography{../../Library}{}
\bibliographystyle{alphaurl}

\printnomenclature

>>>>

    The surface of $\vec{d}$ as $p_x,p_y$ varies is somewhat distorted
    (fig~\ref{fig:BerryPhase/Shape}). Thankfully, it does not change as $m$
    varies (fig~\ref{fig:BerryPhase/AsMVaries}). Also, it is easy to see that
    when $m<0$ or $m>4$, the surface does not cut the $xy$ plane, hence in that
    region the Berry Phase is trivial. The distorted picture is dispatched into
    4 different pieces in fig~\ref{fig:BerryPhase/attempts}. It could be
    imagined that the vector $\vec{d}$ goes in the order: red
    $\to$blue$\to$yellow$\to$green$\to$red. With this and a little bit of
    imagination, I think the solid angle $\Omega$ when $0<m<2$ and $2<m<4$ are
    both $4\pi$.

    Exact value can be found using the formula for solid angle in a
    parameterized surface. Assuming the surface is parameterized as
    \begin{equation}
        \vec{f}(x,y) = (f_1(x,y), f_2(x,y), f_3(x,y))
    \end{equation}
    Its solid angle can be calculated by:
    \begin{equation}
        \int\dd{x}\dd{y} \frac{\vec{f}(x,y)}{\abs{\vec{f}(x,y)}^3}
        \partial_x \vec{f}(x,y) \cross \partial_y \vec{f}(x,y)
    \end{equation}
    This formula can be understood mathematically
    \cite{SolidAngleParameterizedSurface}, and calculated physically (see p.216 of
    \cite{Shen2012}).  The calculated result for different $m$ is plotted in
    fig~\ref{fig:BerryPhase/SSQFormulaPlot}.
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.5\linewidth]{pics/BerryPhase/Shape.pdf}
        \caption{Surface formed as $p_x,p_y$ varies}
        \label{fig:BerryPhase/Shape}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/AsMVaries.pdf}
        \caption{As $m$ varies, the shape does not change. The blue plane is the
        $xy$ plane. The center of that surface meets the $xy$-plane when $m=2$.
        That surface leaves the $xy$-plane when $m<0$ or $m>4$.}
        \label{fig:BerryPhase/AsMVaries}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/attempts.pdf}
        \caption{Attempts to determine the Berry phase by dispatching the surface
        into 4 different patches ($m=2$)}
        \label{fig:BerryPhase/attempts}
    \end{figure}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/BerryPhase/SSQFormulaPlot.pdf}
        \caption{Plot of Chern Number for different $m$.}
        \label{fig:BerryPhase/SSQFormulaPlot}
    \end{figure}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

\bibliography{../../Library}{}
\bibliographystyle{alphaurl}
\printnomenclature
